Verified Time Balancing of Security Protocols \\ \large A Case Study

### 2018-12-20 Src/paper.tex
Finished initial modelling of simplified protocol

          whichis only used on devices that send hello, 

@@

    \item Let $kc$ reresent the number of key agreement types.

@@

    \item Let $hvi$ represent the initatiors hash value where:

@@

        \item Let $||$ denote bitwise concatenation.

@@

          of the intiators second retained shared secret.
    \item Let $auxi$ represet the auxiliary shared secret.

@@

  a constant time, and thus possibly be ommited for the purpose of

@@

  while $h3$ can be precalculated, it is important for the responder

@@

@@

        \item Let $dh2i$ represent the precalculation of the DH Part 2 message
              by the initator in order to compute part of the $hvi$.

@@

  \subsubsection{Bob precalculates DH Part 2}
  $bob_1=(h3_{b0},pvi)$

@@

>>>>

          which is only used on devices that send hello, 

@@

    \item Let $kc$ represent the number of key agreement types.

@@

    \item Let $hvi$ represent the initiators hash value where:

@@

        \item Let $||$ denote bit-wise concatenation.

@@

          of the initiators second retained shared secret.
    \item Let $auxi$ represent the auxiliary shared secret.

@@

  a constant time, and thus possibly be omitted for the purpose of

@@

  while $h3$ can be pre-calculated, it is important for the responder

@@

  \subsection{The Commit Message} \label{commit}

@@

        \item Let $dh2i$ represent the calculation of the DH Part 2 message
              by the initiator in order to compute part of the $hvi$.

@@

  \subsubsection{Bob pre-calculates DH Part 2}
  $bob_1=(h1_{b0},pvi)$

@@

  The DH Part 1 message is composed primarily of book keeping parameters
  regarding previous shared secrets between the responder and initiator. These
  details will be omitted in this simplified model in the interest of brevity as
  they do not require any computing beyond a simple looking and hash.
    \item Let $pvr$ represent the responders public hash value under the DH3k
      key agreement type where:
        \item Let $svr$ represent a random 3072 bit number under the DH3k key
        \item Let $pvr = mod(g^svr, p)$ represent the public value of the
  $alice_1(h1_{a0},pvr)$

  \subsubsection{Bob calculates the DH Result.}
  \[
    bob_3(pvr_{a1},svi_{b1},p_{b1})=
    \begin{cases}
      \text{Terminate Protocol}, &\text{if } pvr_{a1} = p_{b1} \\
      \text{Terminate Protocol}, &\text{otherwise if } pvr_{a1} = p_{b1} - 1 \\
      \text{Let $dhr = mod(pvr_{a1}^{svi_{b1}},p)$}, &\text{otherwise.}
    \end{cases}
  \]
  \subsection{The DH Part 2 Message}
  This message is a mirror of the DH Part 1 Message from the initiators
  viewpoint. The calculation of the $pvi$ is covered under section
  \ref{commit}.

  \subsubsection{Bob sends DH Part 2 to Alice}
  $bob_4(h2_{b0},pvi_{b1})$

  \subsubsection{Alice calculates the DH Result.}
  \[
    alice_2(pvr_{a1},svi_{b1},p_{b1})=
    \begin{cases}
      \text{Terminate Protocol}, &\text{if } pvr_{a1} = p_{b1} \\
      \text{Terminate Protocol}, &\text{otherwise if } pvr_{a1} = p_{b1} - 1 \\
      \text{Terminate Protocol}, &\text{otherwise if } ha(bob_4||alice_0) \neq
      hvi_{b2} \\
      \text{Let $dhr = mod(pvr_{a1}^{svi_{b1}},p)$}, &\text{otherwise.}
    \end{cases}
  \]
